###Part 1: The Distribution of Averages of Exponential Distributions 
#####By Chris Mai 

#####Overview 
The exponential distribution is a probability distribution that describes the time between two events in a Poissson process. Here, I model the sample mean and variance for 1,000 simulations of the average of 40 exponentials. Lamdba=0.2 for this simulation

#####Simulations

#####Sample Mean versus Theoretical Mean:

```{r}
#The expected mean of the exponential distribution is 1/lambda. In this simulation the expected mean is 5 (1/0.2)

nosim<-1000
n<-40
lambda<-0.2

mean(apply(matrix(rexp(nosim*n, lambda), nosim), 1, mean)) #The sample mean is close to 5

#This simulation calcuates the mean of 1,000 simulations. Each simulation is the mean of 40 exponentials with lambda 0.2
histmeans<-apply(matrix(rexp(nosim*n, lambda), nosim), 1, mean)
hist(histmeans,breaks = seq(0, 14, by = .5), main = "Sample Mean of 1,000 averages of 40 exponents")
abline(v=5, col="violetred3", lwd=2)


#This histogram charts the 1,000 simulations, each an average of 40 exponentials. As expected, they are distributed around the expected population mean of 5.
```

#####Sample Variance versus Theoretical Variance: 
```{r}
#The expected variance of the exponential distribution is (1/lambda)^2/n. In this simulation the expected variance is 0.625 (5^2)/40. The sample variance is close to the expected population variance.
var(apply(matrix(rexp(nosim*n, lambda), nosim), 1, mean)) 
```

#####Distribution: 
```{r}
#Here is a chart of a standard normal distrbution
x=seq(-4,4,length=200)
y=dnorm(x,mean=0,sd=1)
plot(x,y,type="l",lwd=2,col="red",main="Standard Normal Distribution")


#With the standard normal distribution and the sample means charted together, it becomes clear that the distribution of sample means is roughly normal 
par(mfrow=c(2,1)) 
plot(density(histmeans), col="cyan4", lwd=2, main="Sample Mean of 1,000 averages of 40 exponents")
plot(x,y,type="l",col="deeppink3",lwd=2,main="Standard Normal Distribution")


#Compare this to the distribution of 1,000 random exponentials, which does not resemble a normal distribution
rands<-rexp(1000,.2)

par(mfrow=c(2,1))
hist(rands, main = "Sample Mean of 1,000 exponents")
plot(x,y,type="l",col="deeppink3",lwd=2, main="Standard Normal Distribution")
```



